Effects of the body force on the evacuation dynamics

### 2020-02-04 paper.tex
cambios menores en conclu

\subfloat[\label{venn_2parameters}]
{\includegraphics[width=0.45\columnwidth]{./venn_2parameters.png}}
\hfill    
\subfloat[\label{venn_3parameters}]
{\includegraphics[width=0.45\columnwidth]{./venn_3parameters.png}
}\\
\caption[width=0.47\columnwidth]{Venn diagrams for the unit-less parameters
appearing in the equation of motion (\ref{eqn_motion}) (see 
Appendix~\ref{appendix1} for details). The sets correspond to 
$\mathcal{A}=\{\tau/m,1/v_d,A\}$, $\mathcal{K}=\{\tau/m,B,\kappa\}$ and 
$\mathcal{K}_c=\{\tau/m,1/v_d,B,k\}$. (a) The Venn diagram representation if no 
body force is introduced in the SFM (only sets $\mathcal{A}$ and $\mathcal{K}$, 
as in Ref.~\cite{dorso_2019}). (b) The Venn diagram representation for the sets 
$\mathcal{A}$, $\mathcal{K}$ and $\mathcal{K}_c$. }
\label{venn_diagram}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./degree_vs_vd_multi_kn.eps}\label{degree_vd}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./overlap_vs_vd_multi_kn.eps}\label{overlap_vd}}\\
\caption[width=0.47\columnwidth]{(a) Mean degree as a function of the pedestrian’s desired velocity (m/s). (b) Mean overlap as a function of the pedestrians desired velocity. Each symbol indicates the $k_n$ value corresponding to the body force (see the labels). The data corresponds to a bottleneck with periodic boundary conditions (re-injecting pedestrians). The average was taken every two seconds once the crowd reaches the stationary state ($t=$20~s) until the end of the simulation ($t=$110~s).}
\label{degree_overlap_vd}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd2_kn0.eps}\label{network_vd2_kn0}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn0.eps}\label{network_vd10_kn0}}\\
        \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd2_kn1200000.eps}\label{network_vd2_kn1200000}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn1200000.eps}\label{network_vd10_kn1200000}}\\
\caption[width=0.47\columnwidth]{Contact networks of a 225 pedestrian evacuation through a bottleneck. The door is placed at $(x,y)=(20,10)$~m, the width of the door is 0.92~m (equivalent to 2 pedestrian\textsc{\char13}s diameter). The lines that connect the nodes (pedestrians) represent the contact between them. The color represents the degree (the number of pedestrians with which it is connected). (a) and (b) correspond to a simulation without body force with $v_d=$2 and $v_d=$10 respectively. (c) and (d) correspond to simulations with $k_n$=1.2~E6 with $v_d=$2 and $v_d=$10 respectively.}
\label{network_bottleneck}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./degree_vs_dens_multi_kn.eps}\label{degree_dens}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./overlap_vs_dens_multi_kn.eps}\label{overlap_dens}}\\
\caption[width=0.47\columnwidth]{(a) Mean degree as a function of the global density for different $k_n$ values. (b) mean overlap as a function of the global density. The mean values are averages over all the pedestrians and over time once the system reaches the stationary state. Both measurements correspond to corridor geometry with desired velocity $v_d=1$.}
\label{network_corridor}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_d6_kn0.eps}\label{network_d6_kn0}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_d6_knE5.eps}\label{network_d6_knE5}}\\
\caption[width=0.47\columnwidth]{Contact network of the pedestrians along the corridor. The lines that connect the nodes (pedestrians) represent the contact between them. The colors stand for the degree of the node (the number of pedestrians that are in contact with him/her). The corridor was 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$. (a) corresponds to a simulation without body force and (b) corresponds to a simulation with $k_n=1.2$~E5.}
\label{network_corridor}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./vx_profile.eps}\label{vx_profile}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./strain_rate_vs_kn.eps}\label{strain_rate_vs_kn}}\\
\caption[width=0.47\columnwidth]{(a) Velocity in the $x$ coordinate as a function of the transversal coordinate $y$ for three different stiffness values $k$ (see the label). (b) Strain rate as a function of the stiffness level $k_n$ for three different global density values (see label). The measurements correspond to a corridor of 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$. The global density was 7 p~m$^{-2}$.  }
\label{profile_strain}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_nobodyforce.eps}\label{flow_density_no_body_force}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_bodyforce.eps}\label{flow_density_body_force}}\\
\caption[width=0.47\columnwidth]{Flow vs. global density. The flow is calculated in a circular area of R=1~m at the center of the corridor. The circular markers correspond to the original friction of the SFM, the "+" symbol corresponds to the friction increased by a factor of five and the triangles correspond to the friction increased by a factor of ten. The desired velocity was $v_d=1$ in all the cases. (a) corresponds to simulations without body force ($\mathcal{K}_c =$0) and (b) corresponds to a body force with the original value of the body stiffness ($\mathcal{K}_c =$68).}
\label{flow_density}
\end{figure}

>>>>

\subfloat[\label{venn_2parameters}]
{\includegraphics[width=0.49\columnwidth]{./venn_2parameters.png}}
\hfill    
\subfloat[\label{venn_3parameters}]
{\includegraphics[width=0.49\columnwidth]{./venn_3parameters.png}
}\\
\caption[width=0.47\columnwidth]{Venn diagrams for the unit-less parameters
appearing in the equation of motion (\ref{eqn_motion}) (see 
Appendix~\ref{appendix1} for details). The sets correspond to 
$\mathcal{A}=\{\tau/m,1/v_d,A\}$, $\mathcal{K}=\{\tau/m,B,\kappa\}$ and 
$\mathcal{K}_c=\{\tau/m,1/v_d,B,k\}$. (a) The Venn diagram representation if no 
body force is introduced in the SFM (only sets $\mathcal{A}$ and $\mathcal{K}$, 
as in Ref.~\cite{dorso_2019}). (b) The Venn diagram representation for the sets 
$\mathcal{A}$, $\mathcal{K}$ and $\mathcal{K}_c$. }
\label{venn_diagram}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./degree_vs_vd_multi_kn.eps}\label{degree_vd}}\ 
    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./overlap_vs_vd_multi_kn.eps}\label{overlap_vd}}\\
\caption[width=0.47\columnwidth]{(a) Mean degree as a function of the pedestrian’s desired velocity (m/s). (b) Mean overlap as a function of the pedestrians desired velocity. Each symbol indicates the $k_n$ value corresponding to the body force (see the labels). The data corresponds to a bottleneck with periodic boundary conditions (re-injecting pedestrians). The average was taken every two seconds once the crowd reaches the stationary state ($t=$20~s) until the end of the simulation ($t=$110~s).}
\label{degree_overlap_vd}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./network_vd2_kn0.eps}\label{network_vd2_kn0}}\ 
    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./network_vd10_kn0.eps}\label{network_vd10_kn0}}\\
        \subfloat[]{\includegraphics[width=0.49\columnwidth]{./network_vd2_kn1200000.eps}\label{network_vd2_kn1200000}}\ 
    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./network_vd10_kn1200000.eps}\label{network_vd10_kn1200000}}\\
\caption[width=0.47\columnwidth]{Contact networks of a 225 pedestrian evacuation through a bottleneck. The door is placed at $(x,y)=(20,10)$~m, the width of the door is 0.92~m (equivalent to 2 pedestrian\textsc{\char13}s diameter). The lines that connect the nodes (pedestrians) represent the contact between them. The color represents the degree (the number of pedestrians with which it is connected). (a) and (b) correspond to a simulation without body force with $v_d=$2 and $v_d=$10 respectively. (c) and (d) correspond to simulations with $k_n$=1.2~E6 with $v_d=$2 and $v_d=$10 respectively.}
\label{network_bottleneck}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./degree_vs_dens_multi_kn.eps}\label{degree_dens}}\ 
    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./overlap_vs_dens_multi_kn.eps}\label{overlap_dens}}\\
\caption[width=0.47\columnwidth]{(a) Mean degree as a function of the global density for different $k_n$ values. (b) mean overlap as a function of the global density. The mean values are averages over all the pedestrians and over time once the system reaches the stationary state. Both measurements correspond to corridor geometry with desired velocity $v_d=1$.}
\label{network_corridor}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./network_d6_kn0.eps}\label{network_d6_kn0}}\ 
    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./network_d6_knE5.eps}\label{network_d6_knE5}}\\
\caption[width=0.47\columnwidth]{Contact network of the pedestrians along the corridor. The lines that connect the nodes (pedestrians) represent the contact between them. The colors stand for the degree of the node (the number of pedestrians that are in contact with him/her). The corridor was 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$. (a) corresponds to a simulation without body force and (b) corresponds to a simulation with $k_n=1.2$~E5.}
\label{network_corridor}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./vx_profile.eps}\label{vx_profile}}\ 
    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./strain_rate_vs_kn.eps}\label{strain_rate_vs_kn}}\\
\caption[width=0.47\columnwidth]{(a) Velocity in the $x$ coordinate as a function of the transversal coordinate $y$ for three different stiffness values $k$ (see the label). (b) Strain rate as a function of the stiffness level $k_n$ for three different global density values (see label). The measurements correspond to a corridor of 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$. The global density was 7 p~m$^{-2}$.  }
\label{profile_strain}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./flow-density_multifric_nobodyforce.eps}\label{flow_density_no_body_force}}\ 
    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./flow-density_multifric_bodyforce.eps}\label{flow_density_body_force}}\\
\caption[width=0.47\columnwidth]{Flow vs. global density. The flow is calculated in a circular area of R=1~m at the center of the corridor. The circular markers correspond to the original friction of the SFM, the "+" symbol corresponds to the friction increased by a factor of five and the triangles correspond to the friction increased by a factor of ten. The desired velocity was $v_d=1$ in all the cases. (a) corresponds to simulations without body force ($\mathcal{K}_c =$0) and (b) corresponds to a body force with the original value of the body stiffness ($\mathcal{K}_c =$68).}
\label{flow_density}
\end{figure}
